Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
add main

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[capitalise]{cleveref}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}

\newtheorem*{theorem*}{Theorem}
\newenvironment{centermath}
 {\begin{center}$\displaystyle}
 {$\end{center}}

@@

\subsection{Stochastic Regular Expression Equivalences}
$\Expand$ needs to be able to find equivalent stochastic regular expressions.
However, existing work does not provide a means to reason about stochastic
regular expression equivalence. We extend the \emph{star-semiring}~\cite{Droste2009}
equivalences to stochastic regular expressions.

\begin{center}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)*\Probability_2}{1 - \Probability_1 * \Probability_2}})}{\Probability_1*\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
\end{center}

@@

\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
\begin{array}[b]{c}
\quad\\
  \inferrule*
  {
  }
  {
    \IdentityLensOf{\BRegex} \OfType \BRegex \Leftrightarrow \BRegex
  }
  \\
  \quad
  \end{array}
&
\begin{array}[b]{r@{\ }c@{\ }l}
    \CreateR{} \App s & = & s\\
    \PutR{} \App s_1 \App s_2 & = & s_1\\
  \end{array}
\end{array}
\end{centermath}
Note that the identity lens ignores the second argument in the put functions.
Because the two formats are fully synchronized, no knowledge of the prior data
is needed.

\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
  \inferrule*
  {
    \String \in \LanguageOf{\BRegex}\\
    \StringAlt \in \LanguageOf{\BRegexAlt}
  }
  {
    \DisconnectOf{\BRegex}{\BRegexAlt}{\String}{\StringAlt}
    \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
&
  \begin{array}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String'$ & = & $\StringAlt$\\
    $\PutR{} \App \String''' \App \StringAlt'$ & = & $\StringAlt'$\\
  \end{array}
\end{array}
\end{centermath}

@@

Concat is similar to concatenation in existing string lens languages like
Boomerang.  For such terms, we do not provide the semantics, and merely refer readers to existing work. The swap combinator is similar to concat, though the second regular expression
is swapped.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\String_2$ & = & $(\Lens_2.\CreateROf{\String_2})(\Lens_1.\CreateROf{\String_1})$\\
%    $\CreateL{} \App \StringAlt_2\StringAlt_1$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_2\StringAlt_1)$ & = & $(\Lens_2.\PutROf{\String_2}{\StringAlt_2})(\Lens_1.\PutROf{\String_1}{\StringAlt_1})$\\
%    $\PutL{} \App (\StringAlt_2\StringAlt_1) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \OrLensOf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
  $
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

    $\PutR{} \App \String \App \StringAlt$
    & =
    & $\begin{cases*}
        \Lens_1.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$\\
        \Lens_2.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[capitalise]{cleveref}
\usepackage{amsmath}
\usepackage{makecell}%To keep spacing of text in tables
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}

\newtheorem*{theorem*}{Theorem}
\newenvironment{centermath}
 {\begin{center}$\displaystyle}
 {$\end{center}}
\setcellgapes{4pt}%parameter for the spacing

@@

\begin{figure}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)*\Probability_2}{1 - \Probability_1 * \Probability_2}})}{\Probability_1*\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
  \caption{Stochastic Regular Expression Star-Semiring Equivalence}
  \label{fig:ssr-sre}
\end{figure}

\subsection{Stochastic Regular Expression Equivalences}
$\Expand$ needs to be able to find equivalent stochastic regular expressions.
However, existing work does not provide a means to reason about stochastic
regular expression equivalence. We extend the
\emph{star-semiring}~\cite{Droste2009} equivalences to stochastic regular
expressions (Figure~\ref{fig:ssr-sre}).

@@

\begin{centermath}
  \begin{tabular}{m{1cm}@{\hspace*{6em}}m{1cm}@{\hspace*{3em}}}
    $
  \inferrule*
  {
  }
  {
    \IdentityLensOf{\BRegex} \OfType \BRegex \Leftrightarrow \BRegex
  }$
&
$\begin{array}[b]{r@{\ }c@{\ }l}
    \CreateR{} \App s & = & s\\
    \PutR{} \App s_1 \App s_2 & = & s_1
  \end{array}$
\end{tabular}
\end{centermath}
Note that the identity lens ignores the second argument in the put functions.
Because the two formats are fully synchronized, no knowledge of the prior data
is needed.

\begin{centermath}
  \begin{tabular}{m{5cm}m{2cm}}
    $
    \inferrule*
    {
    \String \in \LanguageOf{\BRegex}\\
    \StringAlt \in \LanguageOf{\BRegexAlt}
    }
    {
    \DisconnectOf{\BRegex}{\BRegexAlt}{\String}{\StringAlt}
    \OfType \BRegex \Leftrightarrow \BRegexAlt
    }$
    &
      $
  \begin{array}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String'$ & = & $\StringAlt$\\
    $\PutR{} \App \String' \App \StringAlt'$ & = & $\StringAlt'$
  \end{array}$
\end{tabular}
\end{centermath}

@@

Concat is similar to concatenation in existing string lens languages like
Boomerang.  For such terms, we do not provide the semantics, and merely refer readers to existing work. The swap combinator is similar to concat, though the second regular expression
is swapped.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\String_2$ & = & $(\Lens_2.\CreateROf{\String_2})(\Lens_1.\CreateROf{\String_1})$\\
%    $\CreateL{} \App \StringAlt_2\StringAlt_1$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_2\StringAlt_1)$ & = & $(\Lens_2.\PutROf{\String_2}{\StringAlt_2})(\Lens_1.\PutROf{\String_1}{\StringAlt_1})$\\
%    $\PutL{} \App (\StringAlt_2\StringAlt_1) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}
\begin{centermath}
  \begin{tabular}{m{5cm}m{7cm}}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \OrLensOf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
  $
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

    $\PutR{} \App \String \App \StringAlt$
    & =
    & $\begin{cases*}
        \Lens_1.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$\\
        \Lens_2.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
\begin{centermath}
  \begin{tabular}{m{5cm}m{6cm}}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

\begin{centermath}
  \begin{tabular}{m{5cm}m{6cm}}
  $
  \inferrule*
  {
    \Lens_1 \OfType \BRegex \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegexAlt \Leftrightarrow \BRegexAltAlt\\
  }
  {
    \ComposeLensOf{\Lens_1}{\Lens_2} \OfType
    \BRegex \Leftrightarrow \BRegexAltAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$ & = & $\Lens_2.\CreateROf{(\Lens_1.\CreateROf{\String})}$\\
    $\CreateL{} \App \StringAlt$ & = & $\Lens_1.\CreateLOf{(\Lens_2.\CreateLOf{\StringAlt})}$\\
    $\PutR{} \App \String \App \StringAltAlt$ & = & $\Lens_2.\PutROf{(\Lens_1.\PutROf{\String}{(\Lens_2.\CreateLOf{\StringAltAlt})})}{\StringAltAlt}$\\
    $\PutL{} \App \StringAltAlt \App \String$ & = & $\Lens_1.\PutLOf{(\Lens_2.\PutLOf{\StringAltAlt}{(\Lens_2.\CreateROf{\String})})}{\String}$
  \end{tabular}
\end{tabular}
\end{centermath}
Composing is interesting in the put functions. Because puts require intermediary
data, we recreate that intermediary data with creates.
